\textbf{On the (non-)exhaustivity of naturally occurring \whqs}

### 2022-10-19 analysis/exploratory/context_versus_nocontext/rscripts/analysis.Rmd
corpus article tex

@@

- We found no significant interactions, except for a two-way interaction between Wh and Task only for who-questions.
- There were significant effects of Wh-Word on the every-paraphrase only for who- and how-, where every-ratings incresased for those Wh compared to When
```{r everyt-para model}
# m.every = lmer(normed_rating ~ cModalPresent*Wh*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id), data=every_data,REML=FALSE)
# saveRDS(m.every, "../models/model-contexts-every.rds")

@@

>>>>

### What
```{r what a}
d_what = a_data %>% 
  filter(Wh=="what") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.a.what = lmer(normed_rating ~ cModalPresent*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_what)
# saveRDS(m.a.what, "../models/a-what.rds")

m.a.what <- readRDS("../models/a-what.rds")
summary(m.a.what)

# m.what.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=d_what)
# summary(m.what.simple)
```

### How
```{r how a}
d_how = a_data %>% 
  filter(Wh=="how") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.a.how = lmer(normed_rating ~ cModalPresent*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_how)
# saveRDS(m.a.how, "../models/a-how.rds")

m.a.how <- readRDS("../models/a-how.rds")
summary(m.a.how)

# m.how.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase|tgrep_id), data=d_how) 
# summary(m.how.simple)
```

### Where
```{r where a model}
d_where = a_data %>% 
  filter(Wh=="where") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.a.where = lmer(normed_rating ~ cModalPresent*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_where) 
# saveRDS(m.a.where, "../models/a-where.rds")

m.a.where <- readRDS("../models/a-where.rds")
summary(m.a.where)

# m.where.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_where) 
# summary(m.where.simple)
```

### Why
```{r why a model}
d_why = a_data %>% 
  filter(Wh=="why") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# table(d_why$workerid,d_why$ModalPresent)

# m.a.why = lmer(normed_rating ~ cModalPresent*cTask + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_why)
# saveRDS(m.a.why, "../models/a-why.rds")

m.a.why <- readRDS("../models/a-why.rds")
summary(m.a.why)

# m.why.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_why) 
# summary(m.why.simple)
```

### Who
```{r who a model}
d_who = a_data %>% 
  filter(Wh=="who") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.a.who = lmer(normed_rating ~ cModalPresent*cTask + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_who) 
# saveRDS(m.a.who, "../models/a-who.rds")

m.a.who <- readRDS("../models/a-who.rds")
summary(m.a.who)

### When
```{r when a model}
# have to use less random effects structure
d_when = a_data %>% 
  filter(Wh=="when") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.a.when = lmer(normed_rating ~ cModalPresent*cTask + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_when)

# saveRDS(m.a.when, "../models/a-when.rds")

m.a.when <- readRDS("../models/a-when.rds")
summary(m.a.when)

# simple effects
# m.when.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase|tgrep_id), data=d_when) 
# summary(m.when.simple)
```

@@

- We found no significant interactions, except for a two-way interaction between Wh and Task only for who-questions.
- There were significant effects of Wh-Word on the every-paraphrase only for who- and how-, where every-ratings incresased for those Wh compared to When
```{r every-para model}
# m.every = lmer(normed_rating ~ cModalPresent*Wh*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id), data=every_data,REML=FALSE)
# saveRDS(m.every, "../models/model-contexts-every.rds")

@@

### What
```{r, what every}
d_what = every_data %>% 
  filter(Wh=="what") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.every.what = lmer(normed_rating ~ cModalPresent*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_what)
# saveRDS(m.every.what, "../models/every-what.rds")

m.every.what <- readRDS("../models/every-what.rds")
summary(m.every.what)

# m.what.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase+cModalPresent|workerid) + (1+paraphrase|tgrep_id), data=d_what)
# summary(m.what.simple)
```

### How
```{r every how}
d_how = every_data %>% 
  filter(Wh=="how") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.every.how = lmer(normed_rating ~ cModalPresent*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_how)
# saveRDS(m.every.how, "../models/every-how.rds")

m.every.how <- readRDS("../models/every-how.rds")
summary(m.every.how)

# m.how.simple = lmer(normed_rating ~ paraphrase*cModalPresent-cModalPresent + (1+paraphrase|tgrep_id), data=d_how) 
# summary(m.how.simple)
```

### Where
```{r where every model}
d_where = every_data %>% 
  filter(Wh=="where") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.every.where = lmer(normed_rating ~ cModalPresent*cTask + (1+cModalPresent|workerid) + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_where)
# saveRDS(m.every.where, "../models/every-where.rds")

m.every.where <- readRDS("../models/every-where.rds")
summary(m.every.where)

# m.where.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_where) 
# summary(m.where.simple)
```

### WHY
```{r why every model}
d_why = every_data %>% 
  filter(Wh=="why") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.every.why = lmer(normed_rating ~ cModalPresent*cTask + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_why)
# saveRDS(m.every.why, "../models/every-why.rds")

m.every.why <- readRDS("../models/every-why.rds")
summary(m.every.why)

# m.why.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase+cModalPresent|workerid) + (1+cParaphrase|tgrep_id), data=d_why) 
# summary(m.why.simple)
```

### Who
```{r who every model}
d_who = every_data %>% 
  filter(Wh=="who") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.every.who = lmer(normed_rating ~ cModalPresent*cTask + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_who)
# saveRDS(m.every.who, "../models/every-who.rds")

m.every.who <- readRDS("../models/every-who.rds")
summary(m.every.who)

### When
```{r when every model}
# have to use less random effects structure
d_when = every_data %>% 
  filter(Wh=="when") %>% 
  mutate(cModalPresent = as.numeric(ModalPresent)-mean(as.numeric(ModalPresent))) %>% 
  mutate(cTask = as.numeric(Task)-mean(as.numeric(Task))) %>% 
  droplevels()

# m.every.when = lmer(normed_rating ~ cModalPresent*cTask + (1+cTask|tgrep_id) + (1+cTask|VerbLemma), data=d_when)
# saveRDS(m.every.when, "../models/every-when.rds")

every.when <- readRDS("../models/every-when.rds")
summary(m.every.when)

# simple effects
# m.when.simple = lmer(normed_rating ~ cParaphrase*cModalPresent-cModalPresent + (1+cParaphrase|tgrep_id), data=d_when) 
# summary(m.when.simple)
```

### 2022-10-19 papers/article/main.tex
corpus article tex

% TASK COEFFICIENT TABLE
\begin{table}
\begin{center} 
\caption{Coefficient table (predicted $\beta$ coefficient, standard error $SE$, $t$ value, and $p$ value) for overall Task x Paraphrase model in metanalaysis comparing Context and NoContext tasks. Both predictors are dummy-coded and centered (0 is no Context and \emph{every}-paraphrase, 1 for Modal is present and \emph{a}-paraphrase.} 
\label{sub-model_res_Task} 
% \vskip .12in
\begin{tabular}{lllll} 
\toprule
{} & $\beta$ & $SE$ & $t$ & $p$\\
\midrule
Intercept & .22 & .003 & 80.66 & $<$.0001\\
Paraphrase & .01 & .006 & 2.26 & $<$.03\\
% \rowcolor{Gainsboro!100}
Task & -.01 & .003 & -4.75 & $<$.0001\\
% \rowcolor{Gainsboro!100}
Paraphrase:Task & .07 & .008 & 8.7 & $<$.0001\\
\bottomrule
\end{tabular} 
\end{center} 
\end{table}

@@

% TASK-A SUBMODEL COEFFICIENT TABLE
\begin{table}
\begin{center} 
\caption{Coefficient table (predicted $\beta$ coefficient, standard error $SE$, $t$ value, and $p$ value) for Task x ModalPresent \emph{wh}-word submodels for the data subsetted to \emph{a}-paraphrases. Both predictors are dummy-coded and centered (0 is no Context, 1 for Modal is present.} 
\label{sub-models_res_Task-a} 
% \vskip .12in
\begin{tabular}{l|lllll} 
\toprule
Wh-Word & {} & $\beta$ & $SE$ & $t$ & $p$\\
\midrule
WHAT & Intercept & .21 & .007 & 31.53 & $<$.0001\\
{} & ModalPresent & .1 & .01 & 11.15 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & Task & .3 & .007 & 4.37 & $<$.0002\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.03 & .01 & -2.86 & $<$.005\\
\bottomrule
\toprule
% HOW & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
HOW & Intercept & .25 & .006 & 42.91 & $<$.0001\\
{} & ModalPresent & .08 & .01 & 6.87 & $<$ .0001\\
% \rowcolor{Gainsboro!100}
{} & Task & .02 & .01 & 2.31 & $<$.05\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & .001 & .01 & .07 & .94\\
% \bottomrule
\toprule
% WHERE & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHERE & Intercept & .22 & .02 & 14.7 & $<$.0001\\
{} & ModalPresent & .1 & .03 & 3.51 & $<$.0006\\
% \rowcolor{Gainsboro!100}
{} & Task & .01 & .02 & .8 & .44\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.02 & .03 & -.75 & .46\\
\bottomrule
\toprule
% {} & WHY & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHY & Intercept & .22 & .007 & 32.84 & $<$.0001\\
{} & ModalPresent & .09 & .02 & 5.82 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & Task & .02 & .01 & 1.27 & .24\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.02 & .02 & -.67 & .5\\
\bottomrule
\toprule
% WHO & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHO & Intercept & .26 & .03 & 9.12 & $<$.0001\\
{} & ModalPresent & .12 & .04 & 2.92 & $<$.005\\
% \rowcolor{Gainsboro!100}
{} & Task & .04 & .01 & 2.87 & $<$.04\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.03 & .04 & -.81 & .42\\
\bottomrule
\toprule
% WHEN & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHEN & Intercept & .27 & .03 & 9.25 & $<$.0001\\
{} & ModalPresent & .22 & .07 & 3.44 & $<$.002\\
% \rowcolor{Gainsboro!100}
{} & Paraphrase & -.01 & .03 & -.31 & .77\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Paraphrase & -.01 & .06 & -.24 & .81\\
\bottomrule
\end{tabular} 
\end{center} 
\end{table}

% TASK-EVERY SUBMODEL COEFFICIENT TABLE
\begin{table}
\begin{center} 
\caption{Coefficient table (predicted $\beta$ coefficient, standard error $SE$, $t$ value, and $p$ value) for Task x ModalPresent \emph{wh}-word submodels for the data subsetted to \emph{every}-paraphrases. Both predictors are dummy-coded and centered (0 is no Context, 1 for Modal is present.} 
\label{sub-models_res_Task-every} 
% \vskip .12in
\begin{tabular}{l|lllll} 
\toprule
Wh-Word & {} & $\beta$ & $SE$ & $t$ & $p$\\
\midrule
WHAT & Intercept & .28 & .02 & 16.09 & $<$.0001\\
{} & ModalPresent & .05 & .02 & 3.05 & $<$.003\\
% \rowcolor{Gainsboro!100}
{} & Task & -.08 & .01 & -6.26 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & .003 & .01 & .22 & .82\\
\bottomrule
\toprule
% HOW & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
HOW & Intercept & .17 & .01 & 14.83 & $<$.0001\\
{} & ModalPresent & -.01 & .01 & -.84 & .4\\
% \rowcolor{Gainsboro!100}
{} & Task & -.04 & .01 & -4.02 & $<$.0007\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.002 & .01 & -.19 & .85\\
% \bottomrule
\toprule
% WHERE & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHERE & Intercept & .19 & .02 & 8.01 & $<$.0001\\
{} & ModalPresent & -.04 & .04 & -.97 & .34\\
% \rowcolor{Gainsboro!100}
{} & Task & -.04 & .01 & -.422 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & .03 & .03 & 1.03 & .3\\
\bottomrule
\toprule
% {} & WHY & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHY & Intercept & .15 & .01 & 17.2 & $<$.0001\\
{} & ModalPresent & -.001 & .02 & -.06 & .95\\
% \rowcolor{Gainsboro!100}
{} & Task & -.03 & .01 & -2.95 & $<$.005\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.01 & .02 & -.62 & .54\\
\bottomrule
\toprule
% WHO & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHO & Intercept & .23 & .02 & 10.35 & $<$.0001\\
{} & ModalPresent & .004 & .07 & .07 & .95\\
% \rowcolor{Gainsboro!100}
{} & Task & -.09 & .02 & -4.2 & $<$.002\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.03 & .05 & -.49 & .62\\
\bottomrule
\toprule
% WHEN & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHEN & Intercept & .16 & .04 & 4.31 & $<$.004\\
{} & ModalPresent & .02 & .06 & .31 & .76\\
% \rowcolor{Gainsboro!100}
{} & Paraphrase & -.02 & .02 & -1.01 & .28\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Paraphrase & .03 & .04 & .71 & .48\\
\bottomrule
\end{tabular} 
\end{center} 
\end{table}

@@

\jd{this next paragraph deserves its own sub-section, should have a heading like "Implications for theories of \whqs", and contain explicit arguments. you can't just claim that the semantic rep is only existential -- you have to say why. you can't just claim that the interpretive process is bayesian -- you have to say why (and in fact, we don't have any evidence to that effect from the data presented here, so it's best to just leave this out, or instead frame as a promising direction for how to excplicitly model in-context reasoning about exhaustivity)}
Givn our results, we argue that the semantic representation of a question is maximally underspecified or really weak, existential in meaning. The interpretive process of resolving that underspecification is Bayesian, and involves joint reasoning about the linguistic signal and its possible alternatives, in addition to the contextual speaker's goal.

>>>>

Table \ref{sub-model_Task} presents regression results assessing the effect of Context (Task) on \emph{a}- and \emph{every}- paraphrase ratings.
{}
% TASK COEFFICIENT TABLE
\begin{table}
\begin{center} 
\caption{Coefficient table (predicted $\beta$ coefficient, standard error $SE$, $t$ value, and $p$ value) for overall Task x Paraphrase model in metanalaysis comparing Context and NoContext tasks. Both predictors are dummy-coded and centered (0 is no Context and \emph{every}-paraphrase, 1 for Modal is present and \emph{a}-paraphrase.} 
\label{sub-model_Task} 
% \vskip .12in
\begin{tabular}{lllll} 
\toprule
{} & $\beta$ & $SE$ & $t$ & $p$\\
\midrule
Intercept & .22 & .003 & 80.66 & $<$.0001\\
Paraphrase & .01 & .006 & 2.26 & $<$.03\\
% \rowcolor{Gainsboro!100}
Task & -.01 & .003 & -4.75 & $<$.0001\\
% \rowcolor{Gainsboro!100}
Paraphrase:Task & .07 & .008 & 8.7 & $<$.0001\\
\bottomrule
\end{tabular} 
\end{center} 
\end{table}

@@

% TASK-A SUBMODEL COEFFICIENT TABLE
\begin{table}
\begin{center} 
\caption{Coefficient table (predicted $\beta$ coefficient, standard error $SE$, $t$ value, and $p$ value) for Task x ModalPresent \emph{wh}-word submodels for the data subsetted to \emph{a}-paraphrases. Both predictors are dummy-coded and centered (0 is no Context, 1 for Modal is present.} 
\label{sub-models_Task-a} 
% \vskip .12in
\begin{tabular}{l|lllll} 
\toprule
Wh-Word & {} & $\beta$ & $SE$ & $t$ & $p$\\
\midrule
WHAT & Intercept & .21 & .007 & 31.53 & $<$.0001\\
{} & ModalPresent & .1 & .01 & 11.15 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & Task & .3 & .007 & 4.37 & $<$.0002\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.03 & .01 & -2.86 & $<$.005\\
\bottomrule
\toprule
% HOW & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
HOW & Intercept & .25 & .006 & 42.91 & $<$.0001\\
{} & ModalPresent & .08 & .01 & 6.87 & $<$ .0001\\
% \rowcolor{Gainsboro!100}
{} & Task & .02 & .01 & 2.31 & $<$.05\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & .001 & .01 & .07 & .94\\
% \bottomrule
\toprule
% WHERE & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHERE & Intercept & .22 & .02 & 14.7 & $<$.0001\\
{} & ModalPresent & .1 & .03 & 3.51 & $<$.0006\\
% \rowcolor{Gainsboro!100}
{} & Task & .01 & .02 & .8 & .44\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.02 & .03 & -.75 & .46\\
\bottomrule
\toprule
% {} & WHY & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHY & Intercept & .22 & .007 & 32.84 & $<$.0001\\
{} & ModalPresent & .09 & .02 & 5.82 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & Task & .02 & .01 & 1.27 & .24\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.02 & .02 & -.67 & .5\\
\bottomrule
\toprule
% WHO & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHO & Intercept & .26 & .03 & 9.12 & $<$.0001\\
{} & ModalPresent & .12 & .04 & 2.92 & $<$.005\\
% \rowcolor{Gainsboro!100}
{} & Task & .04 & .01 & 2.87 & $<$.04\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.03 & .04 & -.81 & .42\\
\bottomrule
\toprule
% WHEN & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHEN & Intercept & .27 & .03 & 9.25 & $<$.0001\\
{} & ModalPresent & .22 & .07 & 3.44 & $<$.002\\
% \rowcolor{Gainsboro!100}
{} & Paraphrase & -.01 & .03 & -.31 & .77\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Paraphrase & -.01 & .06 & -.24 & .81\\
\bottomrule
\end{tabular} 
\end{center} 
\end{table}

% TASK-EVERY SUBMODEL COEFFICIENT TABLE
\begin{table}
\begin{center} 
\caption{Coefficient table (predicted $\beta$ coefficient, standard error $SE$, $t$ value, and $p$ value) for Task x ModalPresent \emph{wh}-word submodels for the data subsetted to \emph{every}-paraphrases. Both predictors are dummy-coded and centered (0 is no Context, 1 for Modal is present.} 
\label{sub-models_Task-every} 
% \vskip .12in
\begin{tabular}{l|lllll} 
\toprule
Wh-Word & {} & $\beta$ & $SE$ & $t$ & $p$\\
\midrule
WHAT & Intercept & .28 & .02 & 16.09 & $<$.0001\\
{} & ModalPresent & .05 & .02 & 3.05 & $<$.003\\
% \rowcolor{Gainsboro!100}
{} & Task & -.08 & .01 & -6.26 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & .003 & .01 & .22 & .82\\
\bottomrule
\toprule
% HOW & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
HOW & Intercept & .17 & .01 & 14.83 & $<$.0001\\
{} & ModalPresent & -.01 & .01 & -.84 & .4\\
% \rowcolor{Gainsboro!100}
{} & Task & -.04 & .01 & -4.02 & $<$.0007\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.002 & .01 & -.19 & .85\\
% \bottomrule
\toprule
% WHERE & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHERE & Intercept & .19 & .02 & 8.01 & $<$.0001\\
{} & ModalPresent & -.04 & .04 & -.97 & .34\\
% \rowcolor{Gainsboro!100}
{} & Task & -.04 & .01 & -.422 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & .03 & .03 & 1.03 & .3\\
\bottomrule
\toprule
% {} & WHY & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHY & Intercept & .15 & .01 & 17.2 & $<$.0001\\
{} & ModalPresent & -.001 & .02 & -.06 & .95\\
% \rowcolor{Gainsboro!100}
{} & Task & -.03 & .01 & -2.95 & $<$.005\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.01 & .02 & -.62 & .54\\
\bottomrule
\toprule
% WHO & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHO & Intercept & .23 & .02 & 10.35 & $<$.0001\\
{} & ModalPresent & .004 & .07 & .07 & .95\\
% \rowcolor{Gainsboro!100}
{} & Task & -.09 & .02 & -4.2 & $<$.002\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.03 & .05 & -.49 & .62\\
\bottomrule
\toprule
% WHEN & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHEN & Intercept & .16 & .04 & 4.31 & $<$.004\\
{} & ModalPresent & .02 & .06 & .31 & .76\\
% \rowcolor{Gainsboro!100}
{} & Paraphrase & -.02 & .02 & -1.01 & .28\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Paraphrase & .03 & .04 & .71 & .48\\
\bottomrule
\end{tabular} 
\end{center} 
\end{table}

@@

\jd{this next paragraph deserves its own sub-section, should have a heading like "Implications for theories of \whqs", and contain explicit arguments. you can't just claim that the semantic rep is only existential -- you have to say why. you can't just claim that the interpretive process is bayesian -- you have to say why (and in fact, we don't have any evidence to that effect from the data presented here, so it's best to just leave this out, or instead frame as a promising direction for how to excplicitly model in-context reasoning about exhaustivity)}

\subsection{Implications for semantic theories of}
Givn our results, we argue that the semantic representation of a question is maximally underspecified or really weak, existential in meaning. The interpretive process of resolving that underspecification is Bayesian, and involves joint reasoning about the linguistic signal and its possible alternatives, in addition to the contextual speaker's goal.
